Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Introduction.

The fact that we tunnel inside HTTPS greatly eases the steganography problem.
It's not necessary to generate plausible HTTP, only plausible TLS.
TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
Of course, there are more subtle considerations that go into
making a circumvention HTTPS stream look like an allowed HTTPS stream,
things like packet size and timing, and duration of TCP connections.
These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.

@@

>>>>

Censorship is a daily reality for many Internet users.
Workplaces, schools, and governments use technical and social means
to prevent access to certain information by the network users under their control.
In response, those users use technical and social means
to gain access to the forbidden information.
What has emerged is an ongoing conflict between censor and censored,
with advances on both sides, more subtle evasion being countered by more powerful detection.

In this paper we describe the design and deployment of meek,
a censorship-resistant communication system that aims at defeating
known technical means of censorship.
meek tunnels traffic through HTTP, but does not attempt to look like plaintext HTTP;
it uses HTTPS to hide the contents of communications
while relaying them through a third-party web services that it itself hard to block.
meek is implemented as a Tor pluggable transport~\cite{pt}.
We have done an initial deployment of the system and it is in use
by a small number of users.

@@

meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
Tunnelling inside HTTPS greatly eases the steganography problem:
It's not necessary to generate plausible HTTP, only plausible TLS,
because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
Of course, there are more subtle considerations that go into
making a circumvention HTTPS stream look like an allowed HTTPS stream,
things like packet size and timing, and duration of TCP connections.
These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
